When are Fuzzy Extractors Possible?

### 2014-09-29 info-bounds/FuzzyExtPossibility.tex
working on proof for fuzzy ext impossibility
adding revised proof of fuzzy ext impossibility

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this
work was sponsored by the Department of the Air Force under Air Force
Contract
\#FA8721-05-C-0002.  Opinions,
interpretations, conclusions and recommendations are those of the author
and
are not necessarily endorsed by the United States Government.  Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University and Harvard University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

\begin{abstract}
We characterize when deriving a stable key from a noisy source is possible.  We use the notation of fuzzy extractors introduced by Dodis et al. (Eurocrypt 2004).  The goal is to produce a strong $key$ from a $w$ drawn from a \emph{strong} distribution $W$ and to produce the same when given a nearby $w'$.  A fuzzy extractor is split into two algorithms $\gen$ which produces $key$ along with some helper information $p$ and $\rep$ which takes $w'$ and $p$ to reproduce $key$.  The key must remain strong in the presence of $p$.  The goal is to produce the correct key whenever $\dis(w, w')\le t$.

Ideally, key derivation should be possible whenever a negligible portion of $W$ lies within a ball~(arbitrarily centered) of radius $t$.  We call the maximum weight that lies within any ball of radius $t$ the fuzzy min-entropy of a distribution.  In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

@@

\subsection{Fuzzy Extractors}\label{sec:fuzz extractor}

We recall definitions and lemmas from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with two changes.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08} and we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.  See~\cite{canetti2014key} for discussion.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that
\[
\forall w, w'\in \mathcal{M}, \dis(w, w')\le t \Rightarrow \Pr[(R, P)\leftarrow \gen(w) \wedge \rep(w', P) =R] \ge 1-\delta
\]
where the probability is taken over the coins of $\gen, \rep$.
\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distance results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.  A fuzzy extractor performs two tasks, producing a uniform key and providing error-tolerance.  Traditional, the uniform key is produced by extraction from the original secret $w$ and the error-tolerance is obtained by using a secure sketch.  Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that 
\[
 \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta
 \] 
where the probability is taken over the coins of $\sketch$ and $\rec$.  
\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

\textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.

@@

@@

If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).  We make this intuition formal in the following result.  
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(m^*, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}
\lemref{lem:fuzz necessary} generalizes to interactive protocols, $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  As stated above, fuzzy min-entropy is also a sufficient condition for security in the interactive setting.  However, in the fuzzy extractor~(non-interactive) setting there are many distributions for which no construction is known to be secure and for which no impossibility result is known.  We attempt to bridge this gap in this work.  Our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.

We separate between two types of fuzzy extractors and secure sketches.  The standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions.  This is because we rarely have complete distributions of a physical probability distribution. We call this type of algorithm distribution-oblivious.  We define a new type of algorithm called distribution-aware that is allowed to know the precise distribution to be supported.  We provide a definition for secure sketches~(extendible to fuzzy extractors):

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness} 
\[
\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta\]
 where the probability is taken over the coins of $\sketch$ and $\rec$.  Note correctness is guaranteed only for the support of $W$.
\item \emph{Security} The distribution $W$ is unknown conditioned on $s$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
Note (\sketch, \rec) know the description of $W$ and security only holds for $W$.  When we consider distribution-aware algorithms, we generally assume they are \emph{inefficient}, this seems inherent to use the (possibly)~exponential size distributions.  One possible approach is to allow $(\sketch, \rec)$ an oracle to the probability mass function of $W$.  Our constructions do not work in this setting.\bnote{why am I talking about this?}

@@

A sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.  Skoric et al. previously used universal hash functions to construct secure sketches in the setting of a polynomial number of error patterns~\cite{skoric2009efficient}.

\begin{construction}
\label{cons:universal hash}
Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a universal hash function.  We describe $\sketch, \rec$ as follows:
\begin{itemize}
\item $\sketch(w)$:
\subitem Sample $K\leftarrow \mathcal{K}$.
\subitem Set $p = F(K, w), K$.
\item $\rec(w', y, K)$:
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = y$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}
\begin{lemma}
Let $W$ be a flat distributions with min-entropy $m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-distribution aware secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
\end{lemma}
\begin{proof}
We first argue security.  Fix some $W\in\mathcal{W}$. Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.

@@

\subsection{Arbitary distributions}
The hashing approach outlined above~(\consref{cons:universal hash}) does not extend to arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm outlined above it is necessary to write down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash may completely reveal the point in this setting.

Dealing with non-flat distributions requires a new strategy.  Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.  Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.  In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.  The main issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal independent hash functions.  We describe $\sketch, \rec$ as follows: 
\begin{itemize}
\item $\sketch(w)$:
\subitem If $\Pr[W=w]\le 2^{-(n+\ell)}$
\begin{itemize}
\item Set $p=0, w$.
\end{itemize}
\subitem Else
\begin{itemize}
\item Find $i$ such that $\Pr[W=w]\in L_i$.  
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{itemize}
\item $\rec(w', y)$:
\subitem If $y_0 = 1$, output $y_{1,..., |y|}$.
\subitem Else parse $(i, z, K) = y_{1,..., |y|}$.
\subitem Enumerate $W^* = \{w \in W | \dis(w, w')\le t\}$.
\subitem For all $w^*\in W^*$, if $F(K, w^*) = z$, output $w^*$.
\subitem Output $\perp$.
\end{itemize}
\end{construction}

\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
\begin{proof}
\textbf{Correctness:}  We begin by arguing correctness.  Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions and obtain the theorem statement.  The proof can be carried out for an arbitrary $\ell$.}  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.  Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

@@

\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.  Going forward we will consider specific metric spaces, namely the Hamming metric.
\section{Distribution-Oblivious Sketches}
\label{sec:dist oblivious}

@@

Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to the case of imperfect correctness.

\subsection{Fuzzy min-entropy is not sufficient for secure sketches}
In the previous section, we saw that if a secure sketch is secure for a family of sources, for every distribution over those sources there is a secure sketch.  In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.

\begin{theorem}
\label{thm:imposs sketch}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.  \bnote{finish proof}
\end{theorem}

@@

Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.  This type of distribution is an affine line in space $\mathbb{F}^\gamma$.  Define $V$ as the uniform distribution over all such $W$.  Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$. Fix some $4\le t < \gamma$.
We then show the following:

>>>>

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
%The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.  
Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University and Harvard University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

\begin{abstract}
We characterize when deriving a stable key from a noisy source is possible.  We use the notation of fuzzy extractors introduced by Dodis et al. (Eurocrypt 2004).  The goal is to produce a strong $key$ from a $w$ drawn from a \emph{strong} distribution $W$ and to produce the same when given a nearby $w'$.  A fuzzy extractor is split into two algorithms $\gen$ which produces $key$ along with some helper information $p$ and $\rep$ which takes $w'$ and $p$ to reproduce $key$.  The key must remain strong in the presence of $p$.  The goal is to produce the correct key whenever $\dis(w, w')\le t$.
\anote{there is a big gap between theory and the needs of practice}

We identify a key quantity of a distribution called \emph{fuzzy min-entropy}.  Fuzzy min-entropy measures the maximum probability mass of a distribution that lies within a ball of radius $t$ in the metric space.  Ideally, key derivation should be possible whenever a distribution has fuzzy min-entropy.  In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

@@

\subsection{Fuzzy Extractors for families of distributions}\label{sec:fuzz extractor}

In this section, we define of fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Second in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.  This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  In the \emph{distribution-aware} setting, the algorithms only work for a distribution $W$.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
\begin{enumerate}
\item \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
\item \rep takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.   
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distinguishability results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.  \bnote{do we care about computational fuzzy extractors?} A fuzzy extractor performs two tasks, information-reconciliation and privacy amplification.  The canonical construction is called \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

\textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.

@@

\paragraph{Distribution-aware setting}
We separate between two types of fuzzy extractors and secure sketches.  Because we rarely have complete descriptions of a physical probability distribution the standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions $\mathcal{W}$.  We call this type of algorithm \emph{distribution-oblivious}.  We define a new type of algorithm called distribution-aware that is allowed to know the precise distribution to be supported.  We provide a definition for secure sketches~(extendible to fuzzy extractors):

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} The distribution $W$ is unknown conditioned on $ss$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
The algorithms $(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  When we consider distribution-aware algorithms, we assume they are \emph{inefficient}.  It would be interesting to investigate natural models for specifying distributions that would allow for efficient~(yet generic) distribution-aware constructions of sketches and extractors.

@@

If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).  We make this intuition formal in the following result.  
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}

The proof of \lemref{lem:fuzz necessary} is in \apref{sec:proof fuzz necessary}.
Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
\lemref{lem:fuzz necessary} still applies.  
This means that fuzzy min-entropy is also a necessary condition for interactive solution.  As described in the introduction, it is possible to provide a common key from $w, w'$ in the interactive setting using secure two party computation.

There are many distributions with fuzzy min-entropy for which no in the fuzzy extractor is known to be secure.  There are also no known impossibility results for distributions with fuzzy min-entropy.  Thus, the situation for fuzzy extractors is quite unclear.
As a reminder, our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.  We begin with the simpler distribution-aware setting and then consider the complicated distribution-oblivious setting.

@@

\begin{construction}
\label{cons:universal hash}
Let $F :\mathcal{K}\times \mathcal{M}\rightarrow R$ be a universal hash function.  Let $W$ be a distribution.  We describe $\sketch_W, \rec_W$ as follows:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item Sample $K\leftarrow \mathcal{K}$.
\item Set $p = F(K, w), K$.
\end{enumerate}
\vspace{.3in}
\end{minipage} &
\begin{minipage}{3in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', p = y, K)$
\item Create $W^* = \{w \in W | \dis(w, w')\le t\}$.
\item For $w^*\in W^*$, if $F(K, w^*) = y$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\begin{lemma}
\label{lem:flat hashing}
Let $W$ be a flat distributions with min-entropy $m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-distribution aware secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
\end{lemma}
\begin{proof}
We first argue security.  Fix some $W\in\mathcal{W}$. Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.

@@

\subsection{Secure sketches for all distributions with fuzzy min-entropy}
The hashing approach used for flat~(\consref{cons:universal hash}) does not work for arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm writes down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash completely reveals the point.

Dealing with non-flat distributions requires a new strategy.  Ideally, this strategy should be aware of the density of the current ball and aware that when an original reading comes from a sparse ball it is not necessary to write down many bits.  Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.  In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.  The issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $W$ be a distribution with $\Hfuzz(W)\ge m$.  Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., n+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal independent hash functions.  We describe $\sketch_W, \rec_W$ as follows: 
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item If $\Pr[W=w] \le 2^{-(n+\ell)}$. Set $p=0,w$.
\item Else
\begin{enumerate}
\item Find $i$ such that $\Pr[W=w]\in L_i$.
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{enumerate}
\end{enumerate}
\vspace{.4in}
\end{minipage} &
\begin{minipage}{3in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', y)$
\item If $y_0 = 1$, output $y_{1,..., |y|}$.
\item Else
\begin{enumerate}
\item Parse $(i, z, K) = y_{1,..., |y|}$.
\item $W^* = \{w \in W | \dis(w, w')\le t\}$.
\item For $w^*\in W^*$, if $F(K, w^*) = z$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.

We provide a full proof in \apref{sec:proof of layered hashing}.  The argument is similar to the proof of \lemref{lem:flat hashing}, however, there is an additional step showing that releasing the probability information is not too harmful.  Namely, that an adversary with access to the probability information improves their success by a polynomial factor.  Note we release $n$ levels where $n =\log |\mathcal{M}|$.

\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}

@@

\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space and only cared about the number of neighbors and the size of the metric space.  Going forward we will consider specific metric spaces, namely the Hamming metric.
\section{Impossibility of Distribution-Oblivious Secure Sketches}
\label{sec:dist oblivious}

@@

Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.

\subsection{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious secure sketches}
In the previous section, we saw that if a secure sketch is secure for a family of sources, you must be able to design a secure sketch for every distribution over those sources.  In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.

\begin{theorem}
\label{thm:imposs sketch}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 3 + (\gamma-1) / \log |\mathbb{F}|$.  
\end{theorem}

@@

Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.  This type of distribution is an affine line in space $\mathbb{F}^\gamma$.  Define $V$ as the uniform distribution over all such $W$.  Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$. Fix some $4\le t < \gamma$.
We then show the following~(in \apref{sec:proof secure sketch imposs}):
